---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jobtrackr

<!-- badges: start -->
<!-- badges: end -->

Job hunting is daunting, especially in this market nowadays. Between dozens of 
applications, different statuses, and offers in different cities, it is easy to 
lose track of where everything are.

jobtrackr provides four simple tools to help you organize and analyze your job search.

## Installation

```r
# install.packages("pak")
pak::pak("ADC-405-S26/jobtrackeR")
```

## Functions

- `application_summary()` - counts applications by status and returns your overall response rate
- `days_since_applied()` - calculates how long each application has been waiting and flags ones with no response after a set number of days
- `compare_offers()` - adjusts offer salaries by cost of living so you can compare them fairly across cities
- `pipeline_stage()` - visualizes your full hiring funnel from Applied to Offered

## Example

```{r example, message = FALSE, warning = FALSE}
library(jobtrackr)
data(jobs)
application_summary(jobs)
```

## Dataset

The package includes `jobs`, a simulated dataset of 30 job applications 
with columns for company, position, location, cost of living, status, 
date applied, salary, and source.

```{r}
head(jobs[, c("company", "position", "status", "salary")])
```

## Learn More

For a full walkthrough with real examples and commentary, see the
[Introduction to jobtrackr](https://adc-405-s26.github.io/jobtrackeR/articles/introduction-to-jobtrackr.html)
vignette.