---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jobtrackr

<!-- badges: start -->
<!-- badges: end -->

jobtrackr helps you track, organize, and analyze your job applications.
It provides four simple tools to summarize application statuses, flag
applications with no response, compare offers adjusted for cost of
living, and visualize your hiring pipeline.

## Installation

```r
# install.packages("pak")
pak::pak("ADC-405-S26/jobtrackeR")
```

## Quick Start

```{r example, message = FALSE, warning = FALSE}
library(jobtrackr)
data(jobs)
```

### Summarize your applications
```{r}
application_summary(jobs)
```

### Compare offers by cost of living
```{r}
compare_offers(jobs)
```

For a full walkthrough of all four functions with real examples and
detailed commentary, see the
[Introduction to jobtrackr](https://adc-405-s26.github.io/jobtrackeR/articles/introduction-to-jobtrackr.html)
vignette.