---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jobtrackr

<!-- badges: start -->
<!-- badges: end -->

## The Problem With Job Hunting

It is the spring semester of your senior year. You have been applying
to jobs for weeks — some on LinkedIn, some through referrals, some on
Indeed. Your spreadsheet is a mess. You cannot remember which companies
responded, which ones ghosted you, or whether that offer from Austin is
actually better than the one from San Francisco once you factor in the
cost of living.

This is exactly the problem jobtrackr was built to solve.

jobtrackr is a small R package that helps you track, organize, and
analyze your job applications. It will not find you a job — but it will
help you think clearly about the ones you have already applied for.

## Installation

You can install the development version of jobtrackr from
[GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("ADC-405-S26/jobtrackeR")
```

## Getting Started

First, load the package and the built-in example dataset. The `jobs`
dataset contains 30 simulated job applications across different
companies, locations, and statuses — a realistic snapshot of what a
semester of job hunting looks like.

```{r example, message = FALSE, warning = FALSE}
library(jobtrackr)
data(jobs)
jobs <- jobtrackr::jobs
```

Let us take a quick look at what the data contains:

```{r}
head(jobs)
```

Each row is one application. The columns tell us the company, position,
location, cost of living index for that city, current status, date
applied, estimated salary, and where the listing was found.

## Step 1: Where Do Things Stand?

The first thing any job seeker wants to know is simple: out of
everything I applied to, what actually happened?

`application_summary()` answers that question in one line.

```{r}
application_summary(jobs)
```

## Step 2: Who Has Not Responded Yet?

Waiting is the hardest part of job hunting. But there is a difference
between patiently waiting and being ghosted. `days_since_applied()`
calculates how many days have passed since each application was
submitted, and flags any that have gone more than 21 days with
no response.

```{r}
result <- days_since_applied(jobs, flag_after = 21)
result[result$possibly_ghosted == TRUE,
       c("company", "position", "date_applied", "days_waiting")]
```

## Step 3: Comparing Real Offers

You have received a few offers — congratulations! But a higher salary
does not always mean a better deal. A $95,000 salary in New York City
buys you far less than $85,000 in Austin, Texas.

`compare_offers()` adjusts each offer by the cost of living index of
its city, so you can compare apples to apples.

```{r}
compare_offers(jobs)
```

## Step 4: Seeing the Full Picture

Finally, `pipeline_stage()` gives you a visual summary of your entire
job search funnel — how many applications made it to each stage.

```{r}
pipeline_stage(jobs)
```