---
title: "Introduction to jobtrackr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to jobtrackr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## The Problem With Job Hunting

It is the spring semester of your senior year. You have been applying
to jobs for weeks — some on LinkedIn, some through referrals, some on
Indeed. Your spreadsheet is a mess. You cannot remember which companies
responded, which ones ghosted you, or whether that offer from Austin is
actually better than the one from San Francisco once you factor in the
cost of living.

This is exactly the problem jobtrackr was built to solve.

jobtrackr is a small R package that helps you track, organize, and
analyze your job applications. It will not find you a job — but it
will help you think clearly about the ones you have already applied for.

## Getting Started

First, load the package and the built-in example dataset. The `jobs`
dataset contains 30 simulated job applications across different
companies, locations, and statuses — a realistic snapshot of what a
semester of job hunting looks like.

```{r setup, message = FALSE, warning = FALSE}
library(jobtrackr)
data(jobs)
```

Let us take a quick look at what the data contains:

```{r}
head(jobs)
```

Each row is one application. The columns tell us the company, position,
location, cost of living index for that city, current status, date
applied, estimated salary, and where the listing was found.

## Step 1: Where Do Things Stand?

The first thing any job seeker wants to know is simple: out of
everything I applied to, what actually happened?

`application_summary()` answers that question in one line.

```{r}
application_summary(jobs)
```

Out of 30 applications, exactly one third are still sitting at
"Applied" with no response — and another third ended in rejection.
Only 3 applications (10%) resulted in an offer. The overall response
rate is 66.7%, meaning roughly 2 out of every 3 applications received
some kind of reply. This kind of summary helps you quickly understand
where your job search stands without scrolling through a spreadsheet.

## Step 2: Who Has Not Responded Yet?

Waiting is the hardest part of job hunting. But there is a difference
between patiently waiting and being ghosted. `days_since_applied()`
calculates how many days have passed since each application was
submitted, and flags any that have gone more than 21 days with no
response.

```{r}
result <- days_since_applied(jobs, flag_after = 21)
result[result$possibly_ghosted == TRUE,
       c("company", "position", "date_applied", "days_waiting")]
```

Ten applications have gone over 21 days with no response and are
flagged as possibly ghosted. Companies like Deloitte, Meta, and
Salesforce have been waiting the longest — over 800 days in this
simulated dataset. In a real job search, this list tells you exactly
which applications to either follow up on or move on from. Knowing
you have been ghosted is far better than endlessly wondering.

## Step 3: Comparing Real Offers

You have received a few offers — congratulations! But a higher salary
does not always mean a better deal. A $95,000 salary in New York City
buys you far less than $85,000 in Austin, Texas.

`compare_offers()` adjusts each offer by the cost of living index of
its city, so you can compare apples to apples.

```{r}
compare_offers(jobs)
```

At first glance, Microsoft's offer of $110,000 looks like the clear
winner. But once adjusted for Seattle's cost of living index of 91,
the real purchasing power comes out to $120,879 — still the best.
Accenture's $95,000 in Chicago adjusts to $107,955, and Nike's
$75,000 in Portland adjusts to $88,235. Without this adjustment, you
might overvalue a high nominal salary in an expensive city and
undervalue a modest offer somewhere more affordable.

## Step 4: Seeing the Full Picture

Finally, `pipeline_stage()` gives you a visual summary of your entire
job search funnel — how many applications made it to each stage.

```{r fig.width = 6, fig.height = 4}
pipeline_stage(jobs)
```

The chart shows the biggest drop-off happens between Applied and
Interviewed — only 7 out of 30 applications (23%) led to an interview.
From there, 3 out of 7 interviews (43%) resulted in an offer. This
tells you that the hardest part of this job search is getting in the
door in the first place. If you want more offers, the data says: apply
more strategically, not just more broadly.

## Wrapping Up

jobtrackr will not write your cover letters or prep you for interviews.
What it will do is cut through the noise of a busy job search and show
you clearly what is working and what is not. The four functions work
together as a complete toolkit — summarize your pipeline, flag what
needs attention, compare your real options, and visualize your
progress.

The best job search is an informed one.